Using Scipion for Stream Image Processing at Cryo-EM Facilities

### 2018-09-27 Review/answer_referee.tex

To create a new protocol in \scipion, a single \python file needs to be created. From this file, the system will discover the new protocol and will automatically build
a form and store the protocol related information in a database.
\scipion protocol developers must certainly know \scipion conventions
but they do not need to modify or even understand the existing code.
In  \scipion next version, the abstraction will be increased
since protocols will be implemented as plug-ins,
that is, independent small \python files  that add functionality to the main
\scipion application. The plug-in approach allows parallel development. That is,  
since protocols are implemented independently from the main application
they can be developed and released in parallel by different teams. In this way, support for a new version of \textit{Relion} does not require a new \scipion release but
a release of the independent \textit{Relion} plug-in

\scipion follows a pure workflow approach and therefore, implements pipelines and describes them as a set of interconnected steps (or protocols). In a workflow approach, users (including microscope staff) can reasonably be expected to modify the paths and incorporate new steps using a GUI (graphic user interface). On the contrary, software packages that do not make this separation produce workflows that, in general, are more challenging to create or modify for non programmers.

Another advantage of the workflow approach 
is the improvement of balance load, reproducibility and  provenance (process of tracing and recording the origins of data and its movement between protocols). The first step in a \scipion workflow execution
is to store in a database each of the protocols to be executed as well as how 
outputs of one protocol are attached to the inputs of another protocol. Then, a workflow engine analyzes the stored data and, using as constraint the number of CPUs assigned by the user to the workflow, optimizes the execution, that is, tries to execute as many protocols in parallel as possible. Obviously, the data stored in the database  have enough information to execute each step and therefore guarantee reproducibility and provenance. Additionally, \scipion currently exports a JSON (JavaScript Object Notation) file describing the complete preprocessing workflow used, so that it can be fully reproduced and visualized elsewhere.

### 2018-09-27 Review/2.overall.tex
to home

Another advantage of a clear separation between steps and relationships 
is the improvement of load balance, reproducibility and  provenance (process of tracing and recording the origins of data and its movement between protocols). The first step in a \scipion workflow execution
is to store in a database each of the protocols to be executed as well as how 
outputs of one protocol are attached to the inputs of another protocol. Then, a workflow engine analyzes the stored data and, using as constraint the number of CPUs assigned by the user to the workflow, optimizes the execution, that is, tries to execute as many protocols in parallel as possible. Obviously, the data stored in the database  have enough information to execute each step and therefore guarantee reproducibility and provenance. Additionally, \scipion currently exports a JSON (JavaScript Object Notation) file describing the complete preprocessing workflow used, so that it can be fully reproduced and visualized elsewhere.

>>>>

Another advantage of the workflow approach 
is the improvement of load balance, reproducibility and  provenance (process of tracing and recording the origins of data and its movement between protocols). The first step in a \scipion workflow execution
is to store in a database each of the protocols to be executed as well as how 
outputs of one protocol are attached to the inputs of another protocol. Then, a workflow engine analyzes the stored data and, using as constraint the number of CPUs assigned by the user to the workflow, optimizes the execution, that is, tries to execute as many protocols in parallel as possible. Obviously, the data stored in the database  have enough information to execute each step and therefore guarantee reproducibility and provenance. Additionally, \scipion currently exports a JSON (JavaScript Object Notation) file describing the complete preprocessing workflow used, so that it can be fully reproduced and visualized elsewhere.
